Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
rework eval section

Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward. The predicate $\True$ becomes the prefix range $0.0.0.0/[0..32]$.
%
Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(T0)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{T0}$.
%
Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the set intersection of their constraints.

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
  \vspace{1em}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \vspace{1em}
    \includegraphics[width=.7\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \vspace{1em}
    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
  \end{minipage}%

@@

  \caption{Product graph construction for policy $\True ~\Path~ \CD{\Exit(\text{Peer1}} ~\Prefer~ \CD{\text{Peer2})}$.}
  \label{fig:example-compilation}
  %\vspace{-1em}
\end{figure*}

@@

We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in network literature and in production networks. For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction. Since many topologies have tunable parameters (e.g., the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for our abstraction. We implement a shortest path routing policy over the topology and record the precision of the abstract analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.

@@

Using abstraction allows us to naturally scale network synthesis in \sysname. We evaluate compilation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.

\para{Routing Policy}

@@

The backbone network classifies neighbors into several categories based on commercial relationship and prefers paths through them in order. Similar to the datacenter, it prevents private address space from external neighbors, drops transit traffic between certain peers but not through others, and aggregates internal prefixes at the border of the network.

\para{Network Topology}

For both networks, we use the fix routing policy but scale the size of the underlying topology. For the datacenter networks, we use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods. The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node to separate local and global prefixes. A single abstract node is used for each class of neighbor.

For the backbone networks, we split the network into two parts: a collection of border routers and an internal core. We scale the backbone networks from 10 to 250 routers. The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core. Backbone neighbors are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).

>>>>

Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward. The predicate $\True$ becomes the prefix range $0.0.0.0/[0..32]$.
%
Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(TG)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{TG}$.
%
Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the set intersection of their constraints.

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
  \vspace{1em}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{N1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{N2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \vspace{1em}
    \includegraphics[width=.7\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \vspace{1em}
    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
  \end{minipage}%

@@

  \caption{Product graph construction for policy $\True ~\Path~ \CD{\Exit(\text{N1}} ~\Prefer~ \CD{\text{N2})}$.}
  \label{fig:example-compilation}
  %\vspace{-1em}
\end{figure*}

@@

We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in network literature and in production networks. The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction. Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for the abstraction. We implement a shortest path routing policy over the topology and record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.

@@

Using abstraction allows us to naturally scale network synthesis in \sysname. We evaluate compilation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider. For both types networks, we fix routing policy but scale the size of the underlying topology.

\para{Datacenter}

@@

We use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods. The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node to separate local and global prefixes. A single abstract node is used for each class of neighbor.

\para{Backbone}

The backbone policy classifies neighbors into several categories based on commercial relationship and prefers paths through them in order. Similar to the datacenter, it drops private address space from  neighbors, drops transit traffic between certain peers but not others, and aggregates internal prefixes at the border of the network.

For the backbone networks, we split the network into two parts: a collection of border routers and an internal core. We scale the backbone networks from 10 to 250 routers. The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core with mincut annotation both within the core and between the core and border roles. Backbone neighbors are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).
